Insurance choice, decision assistance, and insurer steering

### 2021-03-24 finals/lunch-and-learn/lunch-learn-202103.Rmd
center video slide
change iframe size
update presentation

# Decisions are hard

<iframe width="560" height="315" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146" frameborder="0" allowfullscreen></iframe>

@@

---
# Outline of talk

@@

>>>>

# Some decisions are hard

.center[
<iframe width="800" height="500" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146&end=271" frameborder="0" allowfullscreen></iframe>
]

@@

---
class: inverse

# Outline of talk

@@

---
# Popularity of the exchanges

.center[
![:scale 85%](aca-enrollment-graph.png)
]

---
class: inverse, center, middle
name: data

# Data

---
class: inverse, center, middle
name: dominated

# Analysis of dominated choices

---
class: inverse, center, middle
name: decision-assist

# Effect of decision assistance

---
# Consumer choice model

Household i's Utility for Plan j<br>

$\begin{eqnarray}U_{ij} &=& \alpha_i \underbrace{p_{ij}}_{cons.\\prem.} \hspace{0.075in} + \hspace{0.075in} \underbrace{x'_{j}}_{obs.\\prod.} \beta \hspace{0.075in} + \hspace{0.075in} \underbrace{d'_{i}}_{dem.\\char.} \varphi \hspace{0.075in} + \hspace{0.075in} \underbrace{\xi_{j}}_{unobs.\\prod.} \hspace{0.075in} + \hspace{0.075in} \underbrace{\epsilon_{ij}}_{error} \nonumber\end{eqnarray}$

where<br>

$\begin{eqnarray*}\alpha_i &=& \alpha + d'_i \gamma \end{eqnarray*}$

$\begin{eqnarray*}\underbrace{p_{ij}}_{cons.\\prem.} &=& \underbrace{r_{i}}_{rating\\ fact.} \underbrace{p_j}_{full\\prem.} \hspace{0.075in} - \hspace{0.075in} \underbrace{\max\{p_b - \mathrm{cap}_i,0\}}_{subsidy} \end{eqnarray*}$

# Consumer choice model

Utility for Outside Option (Uninsured)<br>

$\begin{eqnarray*} U_{i0} &=& \alpha_i \underbrace{\rho_i}_{\textrm{penalty}} \hspace{0.075in} + \hspace{0.075in}  \underbrace{\epsilon_{i0}}_{error} \end{eqnarray*}$

---
class: inverse, center, middle
name: steering

# Analysis of insurer steering
